---
Lab1 from Jasmines R in economics class
---

# Data

Data dictionary: [Syracuse city tax parcel data](https://ds4ps.github.io/Data-Science-Class/DATA/syr_parcels.html) 


```{r}
URL <- "https://raw.githubusercontent.com/DS4PS/Data-Science-Class/master/DATA/syr_parcels.csv"
dat <- read.csv( URL, stringsAsFactors=FALSE )
```

```{r, echo=F}
head( dat, 10 ) 
```

```{r, echo=F}
head( dat$owner, 10 )  # preview a vector
```



# Solutions


## Question 1

*How many tax parcels are in Syracuse (dataset dimensions)?* 

**ANSWER:** 


```{r}
numParcels <- nrow(dat)
print(b)
```





## Question 2

*How many acres of land are in syracuse (sum over a numeric vector)?*

**ANSWER:** 
```{r}
print(sum(dat$acres))
```




## Question 3

*How many vacant BUILDINGS are there in Syracuse (sum over a logical vector)?*

**ANSWER:** 
```{r}
c <- sum(dat$vacantbuil, na.rm=TRUE)
print(c)
```



## Question 4

*What proportion of parcels are tax exempt?*

**ANSWER:** 
```{r}
numTaxExemptParcels <- sum(dat$tax.exempt)
print(numTaxExemptParcels / numParcels)
```



## Question 5

*Which neighborhood contains the most tax parcels (table with one variable)?*

**ANSWER:**
```{r}
table <- table(dat$neighborhood)
print(which.max(table))
```



## Question 6

*Which neighborhood contains the most vacant LOTS (table with two variables)?*

**ANSWER:**
```{r}
table2 <- table(dat$neighborhood, dat$vacantbuil)
print(which.max(table2[, 2]))
```
